\section{Cross-Platform Application Design}
\label{sec:application}

GrabDrop is implemented as two native clients---Android and
Desktop---that interoperate seamlessly via a shared network protocol.

\subsection{Android Client}

The Android client is built with Kotlin and Jetpack Compose
(Material~3), targeting Android~10+ (API~29). Key architectural
components include:

\begin{itemize}[leftmargin=*]
  \item \textbf{Foreground service} (\texttt{GrabDropService}): Hosts
    the camera pipeline, gesture detector, network manager, and overlay
    manager. Runs independently of the UI lifecycle.
  \item \textbf{CameraX}: Provides the \texttt{ImageAnalysis} use case
    for front camera frames at configurable frame rates.
  \item \textbf{MediaPipe tasks-vision} (v0.10.14): Performs hand
    landmark detection on each camera frame, running in
    \texttt{VIDEO} mode for temporal tracking.
  \item \textbf{ONNX Runtime Android} (v1.20.0): Executes the pruned
    and quantized TCN model for gesture classification.
  \item \textbf{MediaProjection}: Captures screenshots on
    \texttt{GRAB} events.
  \item \textbf{Overlay animations}: Window-manager-based overlays
    provide visual feedback (flash on grab, ripple on release, wakeup
    indicator).
\end{itemize}

\subsection{Desktop Client}

The Desktop client is a Python CLI application compatible with Linux,
macOS, and Windows. Its architecture mirrors the Android client:

\begin{itemize}[leftmargin=*]
  \item \textbf{OpenCV}: Camera capture via \texttt{VideoCapture}.
  \item \textbf{MediaPipe Python} (v0.10.14): Hand landmark detection.
  \item \textbf{ONNX Runtime} ($\geq$1.17.0): TCN inference.
  \item \textbf{Platform-specific screenshot tools}: \texttt{spectacle}
    (KDE/Wayland), \texttt{grim} (generic Wayland), \texttt{scrot}
    (X11), \texttt{screencapture} (macOS), or \texttt{mss} (Windows).
  \item \textbf{Tkinter overlays}: Visual feedback indicators.
\end{itemize}

\subsection{Network Protocol}

Both clients share a unified zero-configuration network protocol
operating over the local area network:

\subsubsection{Device Discovery (UDP)}

Each device broadcasts a JSON heartbeat message every 3~seconds via
both multicast (\texttt{239.255.77.88:9877}) and broadcast
(\texttt{255.255.255.255:9877}) for reliability. Messages contain a
unique device ID, device name, and timestamp. Devices not heard from
for 10~seconds are removed from the discovery table.

\subsubsection{Screenshot Transfer (UDP + TCP)}

Upon a \texttt{GRAB} event:
\begin{enumerate}[leftmargin=*]
  \item The sender captures a screenshot and starts a TCP server on a
    random port.
  \item A \texttt{SCREENSHOT\_READY} JSON message is broadcast via UDP,
    containing the TCP port and file size.
  \item When a receiver performs a \texttt{RELEASE} gesture, it connects
    to the sender's TCP server, sends \texttt{"GET\textbackslash n"},
    and receives a 4-byte big-endian length header followed by the raw
    PNG data.
\end{enumerate}

\subsubsection{Retroactive Matching}

To handle network latency, the protocol supports retroactive matching:
if a \texttt{RELEASE} gesture occurs before the screenshot offer
arrives, the release timestamp is recorded and matched against
incoming offers within a 3-second window.

\subsection{Cross-Platform Interoperability}

Android and Desktop clients auto-discover each other on the same LAN
and transfer screenshots transparently. The protocol is
platform-agnostic: any device implementing the UDP/TCP wire format
(Section~7 of the protocol specification) can join the GrabDrop
network.
