\section{Conclusion and Future Work}
\label{sec:conclusion}

We have presented GrabDrop, a cross-platform screenshot sharing system
driven by real-time hand gesture recognition. The system demonstrates
that a lightweight TCN model (87K~parameters), combined with
MediaPipe hand landmark detection and a two-stage power-aware
detection pipeline, can achieve practical gesture recognition accuracy
(89.66\%) while remaining deployable on commodity mobile devices through
structured pruning and INT8 quantization (final model size
$\sim$140\,KB).

The project makes several contributions relevant to the course themes
of AI application in practice: (1)~applying cutting-edge temporal
convolutional architectures to a real-world interaction problem;
(2)~demonstrating the full model lifecycle from data collection through
training, optimization, and edge deployment; and (3)~building a
functional cross-platform system with a zero-configuration network
protocol.

\subsection{Limitations}

Several limitations of the current system warrant acknowledgment. The small test set comprising only 29 samples introduces high variance in the reported accuracy, and a larger, more diverse test set would provide more reliable performance estimates. While structured pruning maintains accuracy at 89.66\%, the limited test set size prevents meaningful differentiation between model variants; knowledge distillation from the original model could potentially improve the pruned model's generalization on larger datasets. The current network protocol transmits screenshots in plaintext without encryption, and TLS/DTLS encryption should be added for production deployment to ensure content security. Finally, the system detects only one hand, precluding the possibility of two-handed gesture vocabularies that could enable richer interaction paradigms.

\subsection{Future Directions}

Several promising directions emerge for future development. Knowledge distillation could be employed to train the pruned model under the supervision of the original model, potentially improving generalization on larger datasets without increasing model size. The gesture vocabulary could be expanded to include additional gestures such as pinch-to-zoom, rotation, or multi-finger taps, enabling richer interaction capabilities. Federated learning could be implemented to allow on-device personalization of the gesture model without requiring users to share raw data, preserving privacy while improving individual user experience. End-to-end encryption through TLS for TCP transfer and DTLS for UDP discovery would secure content during transmission. Finally, incorporating additional modalities such as depth cameras or IMU data could enhance the robustness of gesture recognition in challenging environmental conditions.
